---
title: "Fixed loci CNV calling filtering tree"
author: "Simone Montalbano"
date: "`r lubridate::date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{QC_tree}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The aim of this package is to [...]

# Setup

To install and load the latest version of the package you can
run the following code:

```{r setup}
devtools::install_github("SinomeM/QCtreeCNV")
library(QCtreeCNV)
```

# Data Format

The pipeline require two main input objects:

1. a `data.frame` (bonus if already `data.table`)
   containing the putative CNV carriers calls;   
1. a `data.frame` (bonus if already `data.table`)
   containing the required quality metrics.

Additionally the package will compute CNVRs (starting from
table 1).

We provide functions to create the quality metrics table
starting from:

a. the raw intensity files;   
b. genomic coordinates of the loci of interest;   
c. a table to link samples ID to the raw intensity files.

Specifications on each object is given in the following sections.

## CNV calls

Table 1 consist of the [...]

## Quality metrics / Raw data trends

Table 2 consist of [...]


# Run the Pipeline


# Session

```{r}
sessionInfo()
```

